Statistics in real world applications requires statistical software. We will use the R statistical software for most of our computations and analysis. {\it No prior experience with statistical software or programming is required or assumed}. You will gain familiarity with R through interactive tutorials on the web.  Additionally, you will complete lab assignments that require you to work directly with R.\\

You can access R through a cloud based platform, Posit Cloud (\url{https://posit.cloud/}), where you can register for a free account. Alternatively, you can download and install R onto your personal machine from \url{https://cran.r-project.org/}. Make sure to download the version for your computer (note that newer Macs with M1 chip require the arm64 version) and install like you would other software - by simply clicking on the downloaded installation file. You will also need to download RStudio, which is a workspace environment that we will use for using R, creating documents, and managing your work. (RStudio comes automatically with the Posit Cloud version of R), You can download RStudio at \url{https://posit.co/downloads/}. You should download and install R first, before installing RStudio. See the videos linked below for step by step instruction.\\

I recommend installing on your machine if that is possible, but either of these options is acceptable, and you can even do both. One advantage of the Posit Cloud version is that you can use it with chromebook type devices. Of course, you will need an internet connection to use it.  % it does not require installing software on your machine, and there  The disadvantages are that it is a bit little slower with some functionality, there are usage and data limitations (though for this course we wont have to worry about that), and there is an added step of downloading/uploading as you transfer documents between Brightspace, your machine, and Posit Cloud. \\

%The advantages of the desktop version are that you dont need an internet connection to use it, it is yours to use freely for life, and it will be convenient if you ever want to use R for other projects; perhaps in other classes.  \\


These videos  step you through the processs for installing on a personal machine:\\
For Mac: \url{https://www.youtube.com/watch?v=AEebOXiMyyI}\\
For Windows: \url{https://www.youtube.com/watch?v=rHZ9MGWxU5I&t=0s}\\


{\bf You should either install R and RStudio on your machine or register on Posit Cloud, before our first class}. \\

We will use R often in the classroom, so you should bring a laptop or device to class. (Chromebooks work but tablet devices are not so great. You really need a keyboard.) {\bf If you do not have access to a personal machine or device please let me know as soon as possible so that we can try to make arrangements for a loaner machine.}




