{\bf Required}
\begin{itemize}
\item {\it Introduction to Statistical Learning with Applications in R}.  James, Witten, Hastie, Tibshirani, 2013. Free electronically. Is the more ``accessible” version of the “Elements” below. \url{http://faculty.marshall.usc.edu/gareth-james/ISL/}
\item {\it Elements of Statistical Learning}, Hastie, Tibshirani, Friedman. Springer,  Another free book. This book gives a full-blown treatment. Heavy on the mathematics. \url{https://web.stanford.edu/~hastie/ElemStatLearn/}
%\item {\it R for Data Science}, by Grolemund and Wickham, This book is free electronically  It is a non-mathematical introduction to data manipulation and visualization in R. \url{https://r4ds.had.co.nz/index.html}
\end{itemize}

{\bf Additional recommended}
\begin{itemize}
\item {\it Practical Regression and ANOVA Using R}, Faraway, 2002. Free electronic
\item{\it Applied Predictive Modeling} M. Kuhn, K. Johnson, Springer, 2013.
\item {\it R for Data Science}, by Grolemund and Wickham, This book is free electronically  It is a non-mathematical introduction to data manipulation and visualization in R. \url{https://r4ds.had.co.nz/index.html}
%\item {\it R Cookbook} Teetor. O'Reilly, 2011. 
\item {\it Hands on Programming with R} Grolemund, O'Reilly, 2011. 
%\item others as needed
\end{itemize}

{\bf Statistics review}
\begin{itemize}
%\item {\it  Introduction to Statistical Methods and Data Analysis} Ott and Longnecker (your Applied Stats 1 and 2 text)
\item Penn State Eberly School of Business online notes \url{https://newonlinecourses.science.psu.edu/statprogram/} See STAT 501; Online notes
\item Any intermediate Statistics text. Devore is a good one.
\end{itemize}










 
